Supplementary material to ``Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data''

### 2015-09-18 scirep_version.tex
first stab at making the new maps figure
latest modifications corresponding to the ressubmission to Scirep.

\begin{center}
\begin{figure}
 \subfigure[2010]{\includegraphics[width=8cm, 
height=4.82cm]{./plots/heatmap2010.jpg}
% heatmap2010.jpg: 1075x589 pixel, 96dpi, 28.44x15.58 cm, bb=0 0 806 442
}
  \subfigure[2011]{\includegraphics[width=8cm]{./plots/heatmap2011.jpg}}
  \subfigure[2012]{\includegraphics[width=8cm]{./plots/heatmap2012.jpg}
% heatmap2010.jpg: 1075x589 pixel, 96dpi, 28.44x15.58 cm, bb=0 0 806 442
}
  \subfigure[2013]{\includegraphics[width=8cm]{./plots/heatmap2013.jpg}}
  \caption{{\bf Maps showing the incidence of dengue in the city of Rio de 
Janeiro from 2010 to 2013.} Circles indicate individual notified cases. A 
heatmap is overlayed on the maps showing absolute density of cases.
It can be seen that several areas of the city were affected and no region seems 
to be free of transmission risk.
This suggests that although transmission risk varies spatially, there is 
significant exposure over the entire city.}
  \label{fig:mapas}
\end{figure}
\end{center}

@@

\urlprefix\url{
http://www.sciencedirect.com/science/article/pii/S0140673607616870}.

@@

\bibitem{honorio_temporal_2009}
\bibinfo{author}{Hon\'orio, N.~A.}, \bibinfo{author}{Code\c{c}o, C.~T.},
  \bibinfo{author}{Alves, F.~C.}, \bibinfo{author}{Magalh\~aes, M.} \&
  \bibinfo{author}{Louren\c{c}o-De-Oliveira, R.}
\newblock \bibinfo{title}{Temporal distribution of aedes aegypti in different
  districts of rio de janeiro, {B}razil, measured by two types of traps}.
\newblock \emph{\bibinfo{journal}{Journal of Medical Entomology}}
  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{1001--1014}
  (\bibinfo{year}{2009}).
\newblock \urlprefix\url{http://www.bioone.org/doi/abs/10.1603/033.046.0505}.

@@

\urlprefix\url{
http://www.sciencedirect.com/science/article/pii/S0048969708011509}.

\bibitem{reiner_time-varying_2014}
\bibinfo{author}{Reiner, R.~C.} \emph{et~al.}
\newblock \bibinfo{title}{Time-varying, serotype-specific force of infection of
  dengue virus}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{111}},
  \bibinfo{pages}{E2694--E2702} (\bibinfo{year}{2014}).
\newblock \urlprefix\url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4084484/}.

\bibitem{bacaer_final_2009}
\bibinfo{author}{Baca\"er, N.} \& \bibinfo{author}{Gomes, M. G.~M.}
\newblock \bibinfo{title}{On the final size of epidemics with seasonality}.
\newblock \emph{\bibinfo{journal}{Bulletin of Mathematical Biology}}
  \textbf{\bibinfo{volume}{71}}, \bibinfo{pages}{1954--1966}
  (\bibinfo{year}{2009}).
\newblock
  \urlprefix\url{http://link.springer.com/article/10.1007/s11538-009-9433-7}.

\bibitem{katriel_attack_2012}
\bibinfo{author}{Katriel, G.} \& \bibinfo{author}{Stone, L.}
\newblock \bibinfo{title}{Attack rates of seasonal epidemics}.
\newblock \emph{\bibinfo{journal}{Mathematical Biosciences}}
  \textbf{\bibinfo{volume}{235}}, \bibinfo{pages}{56--65}
  (\bibinfo{year}{2012}).
\newblock

\urlprefix\url{
http://www.sciencedirect.com/science/article/pii/S0025556411001532}.

@@

\bibitem{stallybrass}
\bibinfo{author}{Stallybrass, C.~O.} \emph{et~al.}
\newblock \bibinfo{title}{The principles of epidemiology and the process of
  infection.}
\newblock \emph{\bibinfo{journal}{The Principles of Epidemiology and the
  Process of Infection.}}  (\bibinfo{year}{1931}).

@@

\bibitem{clopper}
\bibinfo{author}{Clopper, C.} \& \bibinfo{author}{Pearson, E.~S.}
\newblock \bibinfo{title}{The use of confidence or fiducial limits illustrated
  in the case of the binomial}.
\newblock \emph{\bibinfo{journal}{Biometrika}} \bibinfo{pages}{404--413}
  (\bibinfo{year}{1934}).

@@

\bibitem{luz_disability_2009}
\bibinfo{author}{Luz, P.~M.}, \bibinfo{author}{Grinsztejn, B.} \&
  \bibinfo{author}{Galvani, A.~P.}
\newblock \bibinfo{title}{Disability adjusted life years lost to dengue in
  {B}razil}.
\newblock \emph{\bibinfo{journal}{Tropical Medicine \& International Health}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{237--246}
  (\bibinfo{year}{2009}).
\newblock

\urlprefix\url{
http://onlinelibrary.wiley.com/doi/10.1111/j.1365-3156.2008.02203.x/abstract}.

\bibitem{duarte_data_2006}
\bibinfo{author}{Duarte, H. H.~P.} \& \bibinfo{author}{Fran\c{c}a, E.~B.}
\newblock \bibinfo{title}{Data quality of dengue epidemiological surveillance
  in belo horizonte, southeastern {B}razil}.
\newblock \emph{\bibinfo{journal}{Revista de Sa\'ude P\'ublica}}
  \textbf{\bibinfo{volume}{40}}, \bibinfo{pages}{134--142}
  (\bibinfo{year}{2006}).
\newblock

\urlprefix\url{
http://www.scielosp.org/scielo.php?script=sci_abstract&pid=S0034-891020060001000
  21&lng=en&nrm=iso&tlng=en}.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{plots/4maps.png}
\end{center}
  \caption{{\bf Maps showing the incidence of dengue in the city of Rio de 
Janeiro from 2010 to 2013 -- Clockwise from top left.} Circles indicate 
individual notified cases. A 
heatmap is overlayed on the maps showing absolute density of cases.
It can be seen that several areas of the city were affected and no region seems 
to be free of transmission risk.
This suggests that although transmission risk varies spatially, there is 
significant exposure over the entire city. Maps were generated with QGIS GIS 
software, from incidence data.}
  \label{fig:mapas}
\end{figure}

@@

@@

\bibitem{honorio_temporal_2009}
\bibinfo{author}{Hon\'orio, N.~A.}, \bibinfo{author}{Code\c{c}o, C.~T.},
  \bibinfo{author}{Alves, F.~C.}, \bibinfo{author}{Magalh\~aes, M.} \&
  \bibinfo{author}{Louren\c{c}o-De-Oliveira, R.}
\newblock \bibinfo{title}{Temporal distribution of aedes aegypti in different
  districts of rio de janeiro, {B}razil, measured by two types of traps}.
\newblock \emph{\bibinfo{journal}{Journal of Medical Entomology}}
  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{1001--1014}
  (\bibinfo{year}{2009}).

@@

\bibitem{reiner_time-varying_2014}
\bibinfo{author}{Reiner, R.~C.} \emph{et~al.}
\newblock \bibinfo{title}{Time-varying, serotype-specific force of infection of
  dengue virus}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{111}},
  \bibinfo{pages}{E2694--E2702} (\bibinfo{year}{2014}).

\bibitem{bacaer_final_2009}
\bibinfo{author}{Baca\"er, N.} \& \bibinfo{author}{Gomes, M. G.~M.}
\newblock \bibinfo{title}{On the final size of epidemics with seasonality}.
\newblock \emph{\bibinfo{journal}{Bulletin of Mathematical Biology}}
  \textbf{\bibinfo{volume}{71}}, \bibinfo{pages}{1954--1966}
  (\bibinfo{year}{2009}).

\bibitem{katriel_attack_2012}
\bibinfo{author}{Katriel, G.} \& \bibinfo{author}{Stone, L.}
\newblock \bibinfo{title}{Attack rates of seasonal epidemics}.
\newblock \emph{\bibinfo{journal}{Mathematical Biosciences}}
  \textbf{\bibinfo{volume}{235}}, \bibinfo{pages}{56--65}
  (\bibinfo{year}{2012}).

@@

\bibitem{stallybrass}
\bibinfo{author}{Stallybrass, C.~O.} \emph{et~al.}
\newblock \emph{\bibinfo{title}{The Principles of Epidemiology and the Process
  of Infection}}, vol.~\bibinfo{volume}{4} of \emph{\bibinfo{series}{10}}
  (\bibinfo{publisher}{George Routledge \& Son, Ltd.}, \bibinfo{year}{1931}),
  \bibinfo{edition}{1} edn.

@@

\bibitem{clopper}
\bibinfo{author}{Clopper, C.} \& \bibinfo{author}{Pearson, E.~S.}
\newblock \bibinfo{title}{The use of confidence or fiducial limits illustrated
  in the case of the binomial}.
\newblock \emph{\bibinfo{journal}{Biometrika}} \textbf{\bibinfo{volume}{26}},
  \bibinfo{pages}{404--413} (\bibinfo{year}{1934}).

@@

\bibitem{luz_disability_2009}
\bibinfo{author}{Luz, P.~M.}, \bibinfo{author}{Grinsztejn, B.} \&
  \bibinfo{author}{Galvani, A.~P.}
\newblock \bibinfo{title}{Disability adjusted life years lost to dengue in
  {B}razil}.
\newblock \emph{\bibinfo{journal}{Tropical Medicine \& International Health}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{237--246}
  (\bibinfo{year}{2009}).

\bibitem{duarte_data_2006}
\bibinfo{author}{Duarte, H. H.~P.} \& \bibinfo{author}{Fran\c{c}a, E.~B.}
\newblock \bibinfo{title}{Data quality of dengue epidemiological surveillance
  in belo horizonte, southeastern {B}razil}.
\newblock \emph{\bibinfo{journal}{Revista de Sa\'ude P\'ublica}}
  \textbf{\bibinfo{volume}{40}}, \bibinfo{pages}{134--142}
  (\bibinfo{year}{2006}).
